---
title: "Step 4: Obtain aggregated data on temporal symmetry"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{a05_Summarise_temporal_symmetry}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  warning = FALSE,
  message = FALSE,
  collapse = TRUE,
  comment = "#>",
  fig.width = 7,
  fig.height = 5,
  eval = Sys.getenv("$RUNNER_OS") != "macOS"
)
```

# Introduction
In this vignette we will explore the functionality and arguments of `summariseTemporalSymmetry()` function. This function uses `cdm$intersect` introduced in the previous vignettes to produce aggregated statistics containing the frequency for different time gaps between the initiation of the marker and the initiation of the index (`marker_date` $-$ `index_date`) and can be used to then help visulise the asymmetry between the index and marker cohorts. The work of this function is best illustrated via an example. 

```{r message= FALSE, warning=FALSE, include=FALSE}
# Load libraries
library(dplyr)
library(CohortSymmetry)
library(CohortConstructor)
library(omock)

# Get mock data from omock
cdm <- mockCdmFromDataset(datasetName = "GiBleed")

# Generate index-marker cohorts
aspirin_codelist <- CodelistGenerator::getDrugIngredientCodes(
  cdm = cdm,
  name = "aspirin",
  nameStyle = "{concept_name}"
)

cdm[["aspirin"]] <- CohortConstructor::conceptCohort(
  cdm = cdm,
  conceptSet = aspirin_codelist,
  exit = "event_end_date",
  name = "aspirin")


amoxicillin_codelist <- CodelistGenerator::getDrugIngredientCodes(
  cdm = cdm,
  name = "amoxicillin",
  nameStyle = "{concept_name}"
)

cdm[["amoxicillin"]] <- CohortConstructor::conceptCohort(
  cdm = cdm,
  conceptSet = amoxicillin_codelist,
  exit = "event_end_date",
  name = "amoxicillin")

# Generate a sequence cohort
cdm <- generateSequenceCohortSet(
  cdm = cdm,
  indexTable = "aspirin",
  markerTable = "amoxicillin",
  name = "intersect")

```

Recall that in the previous vignette, we've used `cdm$aspirin` and `cdm$acetaminophen` to generate `cdm$intersect`.

# Obtaining temporal symmetry

```{r message= FALSE, warning=FALSE}
summariseTemporalSymmetry(cohort = cdm$intersect, days = 30) |> 
  dplyr::glimpse()
```

The default of the difference of two initiations is measured in 30 days. The estimate value is an aggregate count of how many individuals having the *index* happening **after** *marker* and having the *marker* happening **after** *index*
in 30 day bins.

## Modify `days`

Recall the default for the days is 30, one could also change this to other numerical numbers such as 7, 60, 90 days for example.

```{r message= FALSE, warning=FALSE}
summariseTemporalSymmetry(cohort = cdm$intersect,
                          days = 60) |> 
  dplyr::glimpse()
```

We will use the output from this function to then visulise the asymmetry between the index and marker in the next steps of the vignette.
